### 2019-09-13 upper.tex
general online for k=3 (1)

We leverage the simple algorithm $ON_{k=3}$ that seeks a perfect partition for $k=3$ towards an algorithm for the general online problem.
Note that in the general model, an optimal partition is not a necessarily a perfect partition.
We divide the sequence of requests into phases.
A phase terminates when there is no perfect partition of components after arrival of some request $r$.
We apply requests to $ON_{k=3}$ as before. 
Once the current phase terminates,
we reset all components by removing (forgetting) all revealed edges,
 and then we proceed to the next phase.

>>>>

We leverage the simple algorithm $ON_{k=3}$ that seeks a perfect partition for $k=3$,
towards an algorithm for the general online problem.
Note that in the general model,
an optimal partition is not a necessarily a perfect partition.
We divide the sequence of requests into phases.
A phase terminates when there is no perfect partition of components.
We apply requests to $ON_{k=3}$ as before. 
Once the current phase terminates,
we reset all components by removing (forgetting) all revealed edges,
 and then we proceed to the next phase.
